Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-30 paper/main.tex
rep packag

Our study only examined 24 total source files, from 24 different projects, across four different
languages.  None of these files were very large, though they were of
sizes common to many source files in projects across GitHub, and none
were less than about 100 non-comment lines of code.  More importantly,
there is no simple objective way to determine if a mutation testing
tool is ``as good as'' another tool, in an even approximate sense.
Previous studies of the topic have generally simply expected that a
useful tool must
generate a significant number of non-equivalent unkilled mutants, and
yields mutation scores that are broadly similar to those of other tools.

@@

>>>>

Our study only examined 24 total source files, from 24 different projects, across four different
languages.  None of these files were very large, though they were of
sizes common to many source files in projects across GitHub, and none
were less than about 100 non-comment lines of code.  More importantly,
there is no established way to compare mutation tools.
Previous studies of the topic have generally simply expected that a
useful tool must
generate a significant number of non-equivalent unkilled mutants, and
yield mutation scores that are broadly similar to those of other tools.

\section{Data Availability}

We have made a full replication package available at
\url{https://figshare.com/s/7ab4bc9a156fec248528}.  See the README.md
file included for details.  The package contains Python scripts to run
our data collection and experiments, as well as full source
code for our tool.

@@

\balance
